$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-09-22 paper/paper.tex
Add own work

>>>>

In her master's thesis, Zalakain uses a HOAS to embed a session-typed \picalc{} in Coq \cite{Zalakain2019}.
Channel type polymorphism (preventing channels from being constructed out of thin air) and a process-traversing predicate ensure that channels are used linearly --- subject reduction is then shown to preserve this predicate.
